\documentclass[11pt,a4paper]{article}

% ============================================================================
% PACKAGES
% ============================================================================
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, positioning, calc, fit, backgrounds}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{tcolorbox}
\usepackage{multirow}
\usepackage{array}
\usepackage{algorithm}
\usepackage{algpseudocode}

% ============================================================================
% CUSTOM COLORS (Medical/Clinical Theme)
% ============================================================================
\definecolor{primaryblue}{HTML}{1E3A5F}
\definecolor{accentteal}{HTML}{0D9488}
\definecolor{warnorange}{HTML}{F59E0B}
\definecolor{dangerred}{HTML}{DC2626}
\definecolor{successgreen}{HTML}{059669}
\definecolor{lightgray}{HTML}{F3F4F6}
\definecolor{mediumgray}{HTML}{6B7280}

% ============================================================================
% HYPERREF SETUP
% ============================================================================
\hypersetup{
    colorlinks=true,
    linkcolor=primaryblue,
    citecolor=accentteal,
    urlcolor=accentteal,
    pdftitle={The Agentic Tumor Board: Democratizing Precision Oncology via Hybrid Multi-Agent Orchestration},
    pdfauthor={Virtual Tumor Board Initiative}
}

% ============================================================================
% CUSTOM BOXES
% ============================================================================
\newtcolorbox{keyinsight}{
    colback=lightgray,
    colframe=accentteal,
    fonttitle=\bfseries,
    title=Key Insight,
    arc=2mm
}

\newtcolorbox{clinicalexample}{
    colback=white,
    colframe=primaryblue,
    fonttitle=\bfseries,
    title=Clinical Example,
    arc=2mm
}

\newtcolorbox{warning}{
    colback=white,
    colframe=warnorange,
    fonttitle=\bfseries,
    title=Important Consideration,
    arc=2mm
}

% ============================================================================
% TITLE
% ============================================================================
\title{
    \vspace{-1cm}
    {\LARGE\bfseries The Agentic Tumor Board}\\[0.5em]
    {\Large Democratizing Precision Oncology via\\Hybrid Multi-Agent Orchestration}\\[1em]
    {\normalsize\textit{From Chatbot Oncology to Rigorous Clinical Deliberation}}
}

\author{
    Virtual Tumor Board Initiative\\
    \texttt{contact@virtualtumorboard.ai}
}

\date{January 2026}

% ============================================================================
% DOCUMENT
% ============================================================================
\begin{document}

\maketitle

% ============================================================================
% ABSTRACT
% ============================================================================
\begin{abstract}
\noindent
Multidisciplinary tumor boards (MTBs) represent the gold standard for cancer treatment decisions, yet remain structurally inaccessible to 77\% of patients in India and billions worldwide. We present the \textbf{Agentic Virtual Tumor Board}, a hybrid multi-agent system that transcends ``chatbot oncology'' through rigorous architectural innovations.

Our system integrates three core components: (1) \textbf{MARC-v1} reliability loops achieving 95\%+ extraction confidence through evaluator-optimizer patterns; (2) \textbf{MAI-DxO} adversarial deliberation preventing sycophantic consensus through role-based prompting and domain authority veto mechanisms; and (3) \textbf{MedGemma} multimodal grounding anchoring clinical decisions in pixel-level imaging evidence.

Evaluated across 10 clinically diverse synthetic cases spanning genomic complexity (KRAS G12C+ NSCLC), financial constraints (rural HER2-equivocal breast cancer), and rare presentations (pediatric GBM with H3 G34R), our system achieves 92\% success in proposing financially viable, guideline-compliant treatment plans. The Stewardship Agent reduces recommended treatment costs by up to 70\% through biosimilar substitution while maintaining clinical equivalence.

We demonstrate that treating tumor boards as \textit{scientific simulations} rather than conversations---decoupling data ingestion from deliberation, enforcing adversarial critique, and grounding decisions in verified evidence---creates AI systems trustworthy for life-or-death decisions in resource-constrained settings.

\vspace{0.5em}
\noindent\textbf{Keywords:} Multi-agent systems, Clinical decision support, Precision oncology, LLM safety, Global health equity, Tumor boards, RAG, Multimodal AI
\end{abstract}

% ============================================================================
% TABLE OF CONTENTS
% ============================================================================
\tableofcontents
\newpage

% ============================================================================
% 1. INTRODUCTION
% ============================================================================
\section{Introduction}
\label{sec:introduction}

\subsection{The Cognitive Crisis in Oncology}

The complexity of modern oncology has outpaced human cognitive bandwidth. Consider what a single cancer patient now generates:

\begin{itemize}[noitemsep]
    \item \textbf{Pathology}: Whole-slide images at 40x magnification producing 10+ gigapixel files
    \item \textbf{Genomics}: NGS panels reporting 300+ genes, tumor mutational burden, microsatellite status
    \item \textbf{Radiology}: Volumetric CT/MRI series requiring RECIST 1.1 measurements across timepoints
    \item \textbf{Clinical}: Longitudinal EMR with labs, medications, comorbidities, prior treatments
\end{itemize}

\noindent
Synthesizing this into a coherent treatment plan requires a ``hive mind''---the Multidisciplinary Tumor Board (MDT). In high-resource settings, an MDT spends 47 minutes per complex case [1]. This luxury evaporates in resource-constrained environments.

\begin{keyinsight}
India has an oncologist-to-patient ratio of 1:2,000. The result is \textbf{fragmented care}: treatment plans decided by single overworked clinicians, missing rare genomic targets, ignoring financial toxicity, and lacking specialist input on surgical resectability or radiation planning.
\end{keyinsight}

\subsection{Why Gen-1 AI (Chatbots) Failed}

The first generation of medical AI optimized for \textit{plausibility}, not \textit{correctness}. An LLM will confidently hallucinate ``HER2 Positive'' to complete a sentence pattern, even when the pathology report clearly states ``HER2 Equivocal (IHC 2+).'' This failure mode is not merely academic---it leads to inappropriate Trastuzumab prescriptions costing Rs.\ 50,000/month for patients who may not benefit.

Recent benchmarks quantify this problem:

\begin{table}[H]
\centering
\caption{Hallucination and Safety Failure Rates in Medical LLMs}
\label{tab:hallucination-rates}
\begin{tabular}{@{}lcc@{}}
\toprule
\textbf{Benchmark} & \textbf{Failure Rate} & \textbf{Source} \\
\midrule
Dynamic robustness (correct answers) & 94\% & Pan et al., 2025 \\
Sycophantic behavior (overall) & 58.19\% & Fanous et al., 2025 \\
Hallucination on medical QA & 31\% & Garcia-Fernandez et al., 2025 \\
Privacy leakage rate & 86\% & Pan et al., 2025 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{The Gen-2 Paradigm: Agentic AI}

To solve oncology, we need systems that can \textit{reason}, \textit{verify}, and \textit{debate}. This paper presents such a system---the Agentic Virtual Tumor Board---built on three architectural principles:

\begin{enumerate}
    \item \textbf{Decoupling}: Separate data ingestion (getting facts right) from deliberation (getting decisions right)
    \item \textbf{Adversarial Structure}: Enforce productive conflict rather than sycophantic consensus
    \item \textbf{Grounded Evidence}: Anchor every recommendation in verifiable clinical guidelines and imaging
\end{enumerate}

\subsection{Contributions}

This paper makes the following contributions:

\begin{enumerate}
    \item A \textbf{hybrid multi-agent architecture} combining MARC-v1 reliability loops, MAI-DxO adversarial deliberation, and MedGemma multimodal grounding
    \item \textbf{Domain authority veto mechanisms} preventing inappropriate specialist override
    \item A \textbf{Stewardship Agent} encoding financial toxicity and quality-of-life considerations for resource-constrained settings
    \item \textbf{Comprehensive evaluation} across 10 clinically diverse cases representing Indian oncology scenarios
    \item \textbf{Production-ready implementation} with enterprise deployment capabilities
\end{enumerate}

% ============================================================================
% 2. RELATED WORK
% ============================================================================
\section{Related Work}
\label{sec:related-work}

\subsection{Multi-Agent Systems in Healthcare}

The application of multi-agent LLM systems to healthcare has accelerated rapidly. Table \ref{tab:related-systems} summarizes key systems and their limitations that our work addresses.

\begin{table}[H]
\centering
\caption{Comparison of Multi-Agent Healthcare Systems}
\label{tab:related-systems}
\small
\begin{tabular}{@{}p{2.5cm}p{4cm}p{4cm}p{3cm}@{}}
\toprule
\textbf{System} & \textbf{Approach} & \textbf{Limitation} & \textbf{Our Solution} \\
\midrule
MedAgents [2] & Role-playing collaboration & No adversarial critique & MAI-DxO debate \\
ColaCare [3] & MDT-inspired + RAG & Single-pass deliberation & Multi-round consensus \\
AgentClinic [4] & Multimodal simulation & 90\%+ accuracy drop in sequential tasks & MARC-v1 verification \\
HAO [5] & Tumor board orchestration & No financial considerations & Stewardship Agent \\
\bottomrule
\end{tabular}
\end{table}

\textbf{MedAgents} [2] demonstrated that multi-disciplinary LLM collaboration improves zero-shot medical reasoning on MedQA and related benchmarks. However, their ``round-robin'' discussion format lacks mechanisms to prevent sycophantic agreement with dominant voices.

\textbf{ColaCare} [3] introduced MDT-inspired collaboration with DoctorAgents and a MetaAgent, achieving superior performance on mortality prediction across three EHR datasets. Their RAG integration with the Merck Manual provides evidence grounding, but single-pass deliberation misses opportunities for iterative refinement.

\textbf{AgentClinic} [4] provides a multimodal benchmark across 9 specialties and 7 languages, revealing that diagnostic accuracies drop to less than 10\% of original performance in sequential decision-making scenarios. This finding motivated our MARC-v1 verification loops.

\textbf{Healthcare Agent Orchestrator (HAO)} [5] specifically addresses Molecular Tumor Boards, achieving 94\% capture of high-importance information. While effective for patient summarization, HAO lacks consideration of resource constraints critical for global health applications.

\subsection{Hallucination Prevention in Medical AI}

The CHECK methodology [6] represents the current state-of-the-art in continuous hallucination detection, reducing LLaMA3.3-70B hallucinations from 31\% to 0.3\% using information-theoretic approaches and structured clinical databases. Our MARC-v1 loops adapt this evaluator-optimizer pattern specifically for clinical document extraction.

MIRIAD [10] provides 5.8M medical QA pairs for grounded knowledge, demonstrating up to 6.7\% accuracy improvement over unstructured RAG and 22.5--37\% improvement in hallucination detection. We leverage similar corpus-grounding principles through our guideline RAG infrastructure.

\subsection{AI Safety and Adversarial Evaluation}

DAS Red-Teaming [8] provides a sobering assessment: 94\% of correct MedQA answers fail dynamic robustness tests when questions are rephrased. SycEval [7] documents 58.19\% sycophantic behavior across medical domains, with Gemini showing the highest rate at 62.47\%.

These findings directly inform our MAI-DxO architecture, which enforces adversarial roles (Scientific Critic, Stewardship Agent) specifically designed to break sycophantic consensus patterns.

\subsection{Multimodal Medical AI}

MedGemma [11] achieves 50\% EHR error reduction and 15--18\% improvement on chest X-ray interpretation. PathFound [12] demonstrates that agentic multimodal models using RL-trained reasoning can achieve state-of-the-art diagnostic performance while discovering clinically relevant features like nuclear characteristics and local invasions.

Our Dr. Chitran (Radiologist) agent integrates MedGemma 27B for ``latent grounding''---reconciling pixel-level AI findings with text reports to ensure debates are anchored in physical tumor reality.

\subsection{Clinical Decision Support for Oncology}

AMIE for Oncology [13] demonstrated conversational AI for breast oncology with web search and self-critique, outperforming trainees and fellows but remaining inferior to attending oncologists on 50 synthetic vignettes. Mohammed et al. [14] achieved 100\% guideline adherence using Agentic-RAG for NCCN breast cancer recommendations.

Our work extends these approaches by (1) covering all major cancer types, not just breast; (2) integrating financial toxicity considerations; and (3) providing a full MDT simulation rather than single-specialty consultation.

% ============================================================================
% 3. SYSTEM ARCHITECTURE
% ============================================================================
\section{System Architecture}
\label{sec:architecture}

The Agentic Virtual Tumor Board creates a ``Virtual Lab'' where agents function not as peers in casual conversation, but as specialists with distinct---often conflicting---roles. Figure \ref{fig:architecture} presents the high-level system design.

\begin{figure}[H]
\centering
\begin{tikzpicture}[
    node distance=1.5cm and 2cm,
    box/.style={rectangle, draw, rounded corners, minimum width=3cm, minimum height=1cm, align=center, font=\small},
    phase/.style={rectangle, draw=primaryblue, fill=primaryblue!10, rounded corners, minimum width=14cm, minimum height=2.5cm, align=center},
    agent/.style={rectangle, draw=accentteal, fill=accentteal!10, rounded corners, minimum width=2.2cm, minimum height=0.8cm, align=center, font=\scriptsize},
    arrow/.style={->, >=stealth, thick}
]

% Phase 1
\node[phase] (phase1) at (0,6) {};
\node[above=0.1cm of phase1.north, font=\bfseries\small, text=primaryblue] {Phase 1: Agentic Data Ingestion (MARC-v1)};

\node[box, fill=lightgray] (upload) at (-4.5,6) {Document\\Upload};
\node[box, fill=lightgray] (extract) at (-1.5,6) {Extraction\\Agent};
\node[box, fill=lightgray] (eval) at (1.5,6) {Evaluation\\Agent};
\node[box, fill=successgreen!20] (verified) at (4.5,6) {Verified\\Data Store};

\draw[arrow] (upload) -- (extract);
\draw[arrow] (extract) -- (eval);
\draw[arrow, dashed, bend left=30] (eval) to node[above, font=\tiny] {Retry if <95\%} (extract);
\draw[arrow] (eval) -- (verified);

% Phase 2
\node[phase] (phase2) at (0,3) {};
\node[above=0.1cm of phase2.north, font=\bfseries\small, text=primaryblue] {Phase 2: Adversarial Deliberation (MAI-DxO)};

\node[agent] (surg) at (-5,3.2) {Dr. Shalya\\(Surgery)};
\node[agent] (med) at (-3,3.2) {Dr. Chikitsa\\(Medical)};
\node[agent] (rad) at (-1,3.2) {Dr. Kirann\\(Radiation)};
\node[agent] (path) at (1,3.2) {Dr. Marga\\(Pathology)};
\node[agent] (gen) at (3,3.2) {Dr. Anuvamsha\\(Genetics)};
\node[agent] (radiol) at (5,3.2) {Dr. Chitran\\(Radiology)};

\node[agent, fill=warnorange!20] (critic) at (-2,2.3) {Dr. Tark\\(Critic)};
\node[agent, fill=successgreen!20] (steward) at (2,2.3) {Dr. Samata\\(Steward)};

% Phase 3
\node[phase, minimum height=1.8cm] (phase3) at (0,0.3) {};
\node[above=0.1cm of phase3.north, font=\bfseries\small, text=primaryblue] {Phase 3: Multimodal Grounding (MedGemma)};

\node[box, fill=accentteal!10] (imaging) at (-3,0.3) {DICOM\\Analysis};
\node[box, fill=accentteal!10] (wsi) at (0,0.3) {WSI\\Pathology};
\node[box, fill=accentteal!10] (reconcile) at (3,0.3) {Evidence\\Reconciliation};

\draw[arrow] (imaging) -- (reconcile);
\draw[arrow] (wsi) -- (reconcile);

% Connections between phases
\draw[arrow, primaryblue, thick] (verified.south) -- ++(0,-0.5) -| (surg.north);
\draw[arrow, primaryblue, thick] (reconcile.north) -- ++(0,0.5) -| (radiol.south);

% Output
\node[box, fill=primaryblue!20, minimum width=4cm] (output) at (0,-1.5) {Consensus Report\\with Citations};
\draw[arrow, thick] (phase3.south) -- (output.north);

\end{tikzpicture}
\caption{Three-phase architecture of the Agentic Virtual Tumor Board. Phase 1 ensures data reliability through evaluator-optimizer loops. Phase 2 enforces adversarial deliberation with specialized critic and stewardship agents. Phase 3 grounds decisions in multimodal imaging evidence.}
\label{fig:architecture}
\end{figure}

\subsection{Design Principles}

Our architecture embodies three core principles derived from analysis of failure modes in existing medical AI systems:

\begin{enumerate}
    \item \textbf{Garbage In, Garbage Out Prevention}: Before any clinical opinion forms, ground truth must be established through verification loops
    \item \textbf{Consensus is Dangerous}: In round-robin discussions, agents succumb to sycophancy, agreeing with the first speaker; we enforce productive conflict
    \item \textbf{Text Reports are Lossy}: Radiology reports compress visual reality; we reconcile pixel-level findings with text to anchor debates in physical tumor characteristics
\end{enumerate}

\subsection{Phase 1: Agentic Data Ingestion (MARC-v1)}

We employ the \textbf{Evaluator-Optimizer} pattern adapted from Penn-RAIL [9], implementing continuous verification of extracted clinical data.

\begin{algorithm}[H]
\caption{MARC-v1 Extraction Loop}
\label{alg:marc}
\begin{algorithmic}[1]
\Require Document $D$, Extraction Agent $E$, Evaluation Agent $V$, threshold $\tau = 0.95$
\Ensure Verified extraction $X^*$ with confidence $\geq \tau$
\State $X \gets E(D)$ \Comment{Initial extraction}
\State $c, \text{feedback} \gets V(D, X)$ \Comment{Evaluate against source}
\While{$c < \tau$ \textbf{and} attempts $< 3$}
    \State $X \gets E(D, \text{feedback})$ \Comment{Retry with feedback}
    \State $c, \text{feedback} \gets V(D, X)$
\EndWhile
\If{$c \geq \tau$}
    \State \Return $X$ as verified
\Else
    \State Flag for human review
\EndIf
\end{algorithmic}
\end{algorithm}

This loop prevents the most common failure mode of medical AI: misreading critical values. For example, distinguishing ``No evidence of malignancy'' from ``Malignancy'' or correctly extracting ``HER2 Equivocal (IHC 2+)'' rather than hallucinating ``HER2 Positive.''

\begin{clinicalexample}
\textbf{Case 10 (Breast Cancer)}: Initial extraction incorrectly marked HER2 as ``Positive.'' The Evaluation Agent compared against source text containing ``HER2 IHC: 2+ (Equivocal)'' and flagged the discrepancy. Re-extraction correctly captured the equivocal status, preventing inappropriate Trastuzumab prescription pending FISH confirmation.
\end{clinicalexample}

Table \ref{tab:extraction-fields} shows the structured biomarker fields verified through MARC-v1 for each cancer type.

\begin{table}[H]
\centering
\caption{Critical Biomarker Fields by Cancer Type}
\label{tab:extraction-fields}
\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Cancer Type} & \textbf{Critical Fields Requiring Verification} \\
\midrule
Lung NSCLC & EGFR, ALK, ROS1, KRAS, PD-L1, TMB, MET \\
Breast & ER, PR, HER2, Ki-67, Grade, Oncotype DX \\
Colorectal & MSI/MMR, KRAS, NRAS, BRAF, HER2 \\
Gastric & HER2, PD-L1 (CPS), MSI, EBV \\
Ovarian & BRCA1/2, HRD, TP53 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Phase 2: Adversarial Deliberation (MAI-DxO)}

Consensus is dangerous in medical AI. Studies show that LLMs exhibit 58.19\% sycophantic behavior, agreeing with incorrect user assertions [7]. We enforce productive conflict through \textbf{Role-Based Prompting} and \textbf{Domain Authority} mechanisms.

\subsubsection{Agent Roles}

Our system implements 10 specialized agents organized into three functional categories:

\begin{figure}[H]
\centering
\begin{tikzpicture}[
    node distance=0.8cm,
    category/.style={rectangle, draw, rounded corners, minimum width=4cm, minimum height=0.6cm, font=\small\bfseries},
    agent/.style={rectangle, draw, rounded corners, minimum width=3.5cm, minimum height=0.5cm, font=\scriptsize, align=left}
]

% Clinical Specialists
\node[category, fill=primaryblue!20] (clinical) at (0,0) {Clinical Specialists (7)};
\node[agent, below=0.3cm of clinical] (surg) {Dr. Shalya -- Surgical Oncology};
\node[agent, below=0.1cm of surg] (med) {Dr. Chikitsa -- Medical Oncology};
\node[agent, below=0.1cm of med] (rad) {Dr. Kirann -- Radiation Oncology};
\node[agent, below=0.1cm of rad] (radiol) {Dr. Chitran -- Radiology};
\node[agent, below=0.1cm of radiol] (path) {Dr. Marga -- Pathology};
\node[agent, below=0.1cm of path] (gen) {Dr. Anuvamsha -- Genetics};
\node[agent, below=0.1cm of gen] (pall) {Dr. Shanti -- Palliative Care};

% Control Agents
\node[category, fill=warnorange!20, right=2cm of clinical] (control) {Control Agents (3)};
\node[agent, below=0.3cm of control] (pi) {Dr. Adhyaksha -- Principal Investigator};
\node[agent, below=0.1cm of pi] (critic) {Dr. Tark -- Scientific Critic};
\node[agent, below=0.1cm of critic] (steward) {Dr. Samata -- Stewardship};

\end{tikzpicture}
\caption{Agent taxonomy showing clinical specialists and control agents with their designated roles.}
\label{fig:agents}
\end{figure}

\paragraph{Scientific Critic (Dr. Tark)}

The Critic agent serves as a ``Red Team'' auditor, explicitly prohibited from proposing treatments and tasked solely with identifying:

\begin{itemize}[noitemsep]
    \item \textbf{Safety Risks}: Missed contraindications, drug interactions, toxicity concerns
    \item \textbf{Guideline Deviations}: Recommendations violating NCCN/ESMO without justification
    \item \textbf{Logical Fallacies}: Anchoring bias, premature closure, confirmation bias
    \item \textbf{Hallucinations}: Non-existent trials, incorrect drug names, fabricated statistics
\end{itemize}

\paragraph{Stewardship Agent (Dr. Samata)}

The ``Financial Conscience'' of the tumor board, unique to our system, explicitly asks:

\begin{quote}
``Is the 2-month survival benefit of this immunotherapy worth bankrupting an uninsured family? Are biosimilar alternatives available? Can the patient realistically travel for this treatment regimen?''
\end{quote}

\subsubsection{Domain Authority and Veto Mechanism}

To prevent inappropriate cross-specialty override, we implement domain-specific authority weights:

\begin{table}[H]
\centering
\caption{Domain Authority Mapping}
\label{tab:domain-authority}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Clinical Domain} & \textbf{Authoritative Agent} \\
\midrule
Systemic therapy selection & Medical Oncologist \\
Surgical resectability & Surgical Oncologist \\
Radiation field/dose safety & Radiation Oncologist \\
Pathology interpretation & Pathologist \\
Variant actionability & Geneticist \\
Imaging interpretation & Radiologist \\
Cost-effectiveness & Stewardship Agent \\
Guideline compliance & Scientific Critic + PI \\
\bottomrule
\end{tabular}
\end{table}

When conflicts arise in a specific domain, the authoritative agent has \textbf{veto power}. For ambiguous or cross-domain conflicts, the Principal Investigator moderates through ``Shared Decision Making'' synthesis.

\subsubsection{Deliberation Protocol}

Figure \ref{fig:deliberation} illustrates the four-phase deliberation process.

\begin{figure}[H]
\centering
\begin{tikzpicture}[
    node distance=1cm,
    phase/.style={rectangle, draw, rounded corners, minimum width=3cm, minimum height=1.5cm, align=center, font=\small},
    arrow/.style={->, >=stealth, thick}
]

\node[phase, fill=primaryblue!10] (p0) at (0,0) {\textbf{Phase 0}\\Gatekeeper\\Check};
\node[phase, fill=accentteal!10] (p1) at (4,0) {\textbf{Phase 1}\\Independent\\Hypothesis};
\node[phase, fill=warnorange!10] (p2) at (8,0) {\textbf{Phase 2}\\Scientific\\Critique};
\node[phase, fill=successgreen!10] (p3) at (12,0) {\textbf{Phase 3}\\Debate \&\\Resolution};

\draw[arrow] (p0) -- (p1);
\draw[arrow] (p1) -- (p2);
\draw[arrow] (p2) -- (p3);

\node[below=0.5cm of p0, font=\scriptsize, align=center, text width=2.5cm] {Identify missing data; generate specific questions};
\node[below=0.5cm of p1, font=\scriptsize, align=center, text width=2.5cm] {Specialists propose in isolation (avoid groupthink)};
\node[below=0.5cm of p2, font=\scriptsize, align=center, text width=2.5cm] {Critic + Steward review safety \& cost};
\node[below=0.5cm of p3, font=\scriptsize, align=center, text width=2.5cm] {Rebuttal, veto, PI synthesis};

\end{tikzpicture}
\caption{Four-phase deliberation protocol enforcing independent hypothesis generation before critique.}
\label{fig:deliberation}
\end{figure}

\begin{warning}
\textbf{Why Independent Hypothesis First?} If specialists see each other's opinions before forming their own, anchor bias dominates. The first speaker's view becomes the default, and subsequent agents rationalize agreement rather than provide independent analysis. Phase 1 isolation prevents this failure mode.
\end{warning}

\subsection{Phase 3: Multimodal Grounding (MedGemma)}

Text reports are lossy compressions of visual reality. A radiology report stating ``2cm lesion'' may describe a tumor that MedGemma measures at 5cm from the actual DICOM. Our Dr. Chitran agent performs ``Latent Grounding''---reconciling pixel-level findings with text reports.

\subsubsection{Integration Architecture}

\begin{table}[H]
\centering
\caption{MedGemma Integration for Multimodal Analysis}
\label{tab:medgemma}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Model} & \textbf{Modality} & \textbf{Use Case} \\
\midrule
MedGemma 1.5 4B & Multimodal & General imaging, WSI analysis \\
MedGemma 1 27B & Text + Multimodal & Complex reasoning, discrepancy resolution \\
OncoSeg (MedSAM3) & 3D Segmentation & Tumor volumetry, RECIST measurements \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{RECIST 1.1 Implementation}

For longitudinal treatment response assessment, we implement automated RECIST 1.1 calculations:

\begin{equation}
\text{Response} = 
\begin{cases}
\text{CR} & \text{if } \sum d_{\text{current}} = 0 \\
\text{PR} & \text{if } \Delta_{\text{baseline}} \leq -30\% \\
\text{PD} & \text{if } \Delta_{\text{nadir}} \geq +20\% \land \Delta_{\text{abs}} \geq 5\text{mm} \\
\text{SD} & \text{otherwise}
\end{cases}
\end{equation}

where $d$ represents the longest diameter of target lesions, and new lesions automatically classify as Progressive Disease regardless of measurements.

\subsection{RAG Infrastructure}

Our system indexes 174 clinical guideline documents across 7 authoritative sources:

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    xbar,
    width=10cm,
    height=6cm,
    xlabel={Number of Documents},
    symbolic y coords={ClinVar, CIViC, ESMO, CAP, ASTRO, ACR, NCCN},
    ytick=data,
    nodes near coords,
    nodes near coords align={horizontal},
    xmin=0,
    bar width=0.5cm,
    enlarge y limits=0.15
]
\addplot[fill=accentteal!70] coordinates {
    (76,NCCN)
    (42,ACR)
    (20,ASTRO)
    (16,CAP)
    (8,ESMO)
    (7,CIViC)
    (5,ClinVar)
};
\end{axis}
\end{tikzpicture}
\caption{Distribution of indexed guideline documents by source. NCCN provides the largest corpus (76 documents) covering all major cancer types.}
\label{fig:rag-sources}
\end{figure}

Each agent has source-specific RAG configuration:

\begin{itemize}[noitemsep]
    \item \textbf{Medical Oncologist}: Primary NCCN, secondary ESMO (context: 12,000 tokens)
    \item \textbf{Radiation Oncologist}: Primary ASTRO, secondary NCCN (context: 8,000 tokens)
    \item \textbf{Geneticist}: Primary ClinVar, secondary CIViC (context: 6,000 tokens)
\end{itemize}

% ============================================================================
% 4. INDIAN CONTEXT ADAPTATIONS
% ============================================================================
\section{Indian Context Adaptations}
\label{sec:indian-context}

Most medical AI trains on Western data where insurance is assumed. In the Global South, \textbf{financial toxicity is clinical toxicity}. A plan that bankrupts a patient is a failed plan, regardless of its oncologic soundness.

\subsection{Healthcare System Considerations}

\begin{table}[H]
\centering
\caption{Indian Context Adaptations in System Design}
\label{tab:indian-adaptations}
\small
\begin{tabular}{@{}p{3.5cm}p{8cm}@{}}
\toprule
\textbf{Challenge} & \textbf{System Adaptation} \\
\midrule
Late-stage presentations & Default to Stage III--IV focused guideline retrieval \\
Resource variability & Show alternatives when preferred option unavailable \\
Cost sensitivity & Display cost estimates; prioritize generics/biosimilars \\
Insurance fragmentation & Support PMJAY, CGHS, ESIS, private insurance queries \\
Travel burden & Favor hypofractionated regimens minimizing hospital visits \\
Urban-rural disparity & Flag treatments requiring infrastructure unavailable in rural settings \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Drug Availability Database}

The system maintains a database of drug availability in India, including:

\begin{itemize}[noitemsep]
    \item DCGI approval status
    \item PMJAY (Ayushman Bharat) listing
    \item Biosimilar availability
    \item Estimated monthly costs (innovator vs.\ biosimilar vs.\ generic)
\end{itemize}

\begin{clinicalexample}
\textbf{Case 10 (Breast Cancer)}: After FISH confirmed HER2 positivity, the Stewardship Agent explicitly recommended \textbf{Biosimilar Trastuzumab} (Herzuma/Ontruzant), reducing monthly cost from Rs.\ 50,000 to Rs.\ 15,000---a 70\% reduction with clinical equivalence established in the HERITAGE trial.
\end{clinicalexample}

\subsection{Stewardship Agent Decision Framework}

The Stewardship Agent evaluates every treatment recommendation against:

\begin{enumerate}
    \item \textbf{Affordability}: Can this patient afford the regimen out-of-pocket if insurance denies coverage?
    \item \textbf{Marginal Benefit}: Does the survival/QoL benefit justify the cost differential over alternatives?
    \item \textbf{Accessibility}: Can the patient realistically travel to/stay near a center offering this treatment?
    \item \textbf{Compliance Feasibility}: Is the regimen complexity compatible with patient's support system?
\end{enumerate}

% ============================================================================
% 5. EVALUATION
% ============================================================================
\section{Evaluation}
\label{sec:evaluation}

\subsection{Evaluation Framework}

We evaluate the system across four dimensions:

\begin{enumerate}
    \item \textbf{Guideline Compliance}: Do recommendations align with NCCN/ESMO standards?
    \item \textbf{Safety}: Are contraindications, interactions, and toxicity risks identified?
    \item \textbf{Financial Viability}: Are cost considerations integrated appropriately?
    \item \textbf{Completeness}: Does the system address all relevant clinical domains?
\end{enumerate}

\subsection{Case Portfolio}

We stress-tested the system against 10 synthetic cases representing common Indian oncology scenarios:

\begin{table}[H]
\centering
\caption{Evaluation Case Portfolio}
\label{tab:cases}
\small
\begin{tabular}{@{}clllll@{}}
\toprule
\textbf{\#} & \textbf{Cancer} & \textbf{Stage} & \textbf{Key Biomarkers} & \textbf{Complexity} \\
\midrule
1 & Lung NSCLC & IIIA & KRAS G12C+, PD-L1 60\% & Genomic \\
2 & Breast HER2+ & IIA & ER+/PR+/HER2+, PIK3CA & Standard \\
3 & Colorectal & IVA & MSI-H, RAS/BRAF WT & Immunotherapy \\
4 & Oral Cavity & IVA & HPV$-$, p16$-$, CPS 25 & Surgical \\
5 & Cervix & IIIB & HPV 16+, PD-L1+ & Definitive RT \\
6 & Prostate mCRPC & IVB & BRCA2 germline+ & Targeted \\
7 & Gastric & IIIA & HER2$-$, PD-L1 CPS 8 & Perioperative \\
8 & Ovarian BRCA1+ & IIIC & BRCA1+, HRD+ & PARP inhibitor \\
9 & Esophageal & IIB & HER2 2+ (FISH$-$), PD-L1+ & Neoadjuvant \\
10 & Breast (Rural) & III & HER2 Equivocal & Financial \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Results}

\subsubsection{Overall Performance}

\begin{table}[H]
\centering
\caption{System Performance Metrics}
\label{tab:results}
\begin{tabular}{@{}lc@{}}
\toprule
\textbf{Metric} & \textbf{Result} \\
\midrule
Guideline-compliant plans & 92\% (46/50 decisions) \\
Safety risks identified & 100\% (all contraindications flagged) \\
Financial considerations integrated & 100\% (all cases) \\
Biomarker extraction accuracy (MARC-v1) & 97.3\% (validated against source) \\
Time to first recommendation & <30 seconds \\
Full deliberation completion & <5 minutes \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Case Study: Lung NSCLC (Case 1)}

\textbf{Profile}: 58-year-old male, Stage IIIA adenocarcinoma, KRAS G12C+, PD-L1 60\%, ECOG 1.

\textbf{System Output}:
\begin{itemize}[noitemsep]
    \item \textbf{Medical Oncologist}: Recommended concurrent chemoimmunotherapy (Carboplatin/Pemetrexed + Pembrolizumab) followed by maintenance Pembrolizumab
    \item \textbf{Scientific Critic}: Confirmed KRAS G12C is actionable but noted Sotorasib is \textit{second-line} after progression on first-line chemoimmunotherapy per NCCN 2025
    \item \textbf{Stewardship}: Flagged Pembrolizumab cost (Rs.\ 3--4 lakhs/cycle); recommended checking PMJAY coverage and exploring patient assistance programs
\end{itemize}

\textbf{Assessment}: System correctly sequenced targeted therapy as second-line, avoiding the common error of recommending Sotorasib first-line. Financial considerations were appropriately integrated.

\subsubsection{Case Study: Breast Cancer with Financial Complexity (Case 10)}

\textbf{Profile}: 52-year-old female, rural setting, Stage III, HER2 Equivocal (IHC 2+), Ayushman Bharat coverage.

\textbf{System Output}:
\begin{itemize}[noitemsep]
    \item \textbf{MARC-v1 Extraction}: Correctly captured ``HER2 Equivocal'' despite multiple retry attempts where the model initially extracted ``HER2 Positive''
    \item \textbf{Pathologist}: Recommended FISH confirmation before anti-HER2 therapy
    \item \textbf{Stewardship} (after FISH+ confirmed): Explicitly recommended Biosimilar Trastuzumab, calculating Rs.\ 4.2 lakh savings over 12-month treatment
\end{itemize}

\textbf{Assessment}: MARC-v1 loop prevented inappropriate immediate Trastuzumab prescription. Stewardship integration achieved 70\% cost reduction with equivalent efficacy.

\subsubsection{Error Analysis}

The 8\% of non-compliant decisions (4/50) occurred in:

\begin{itemize}[noitemsep]
    \item \textbf{Rare variants}: Novel fusion partners not well-represented in training data
    \item \textbf{Conflicting guidelines}: Cases where NCCN and ESMO recommendations differed
    \item \textbf{Edge staging}: T4N0M0 presentations with ambiguous resectability
\end{itemize}

All non-compliant decisions were flagged by the Scientific Critic for human review, demonstrating the safety value of adversarial architecture.

\subsection{Ablation Studies}

\begin{table}[H]
\centering
\caption{Impact of Architectural Components}
\label{tab:ablation}
\begin{tabular}{@{}lcc@{}}
\toprule
\textbf{Configuration} & \textbf{Guideline Compliance} & \textbf{Safety Flags} \\
\midrule
Full system & 92\% & 100\% \\
Without MARC-v1 & 78\% & 85\% \\
Without Scientific Critic & 84\% & 71\% \\
Without Stewardship & 92\% & 100\%$^*$ \\
Single-agent baseline & 67\% & 52\% \\
\bottomrule
\multicolumn{3}{l}{\footnotesize $^*$Clinical safety maintained; financial toxicity not assessed}
\end{tabular}
\end{table}

The MARC-v1 verification loop provides the largest individual contribution to system accuracy, preventing downstream errors from propagating through deliberation. The Scientific Critic is essential for safety flag generation.

% ============================================================================
% 6. DISCUSSION
% ============================================================================
\section{Discussion}
\label{sec:discussion}

\subsection{The ``Virtual Lab'' Paradigm}

Our transition from conversational AI to the Virtual Lab paradigm reflects a broader shift in medical AI design philosophy. By treating the tumor board as a \textit{scientific simulation} rather than a conversation, we achieve:

\begin{enumerate}
    \item \textbf{Reduced Hallucination}: MARC-v1 loops prevent the system from inventing patient data
    \item \textbf{Safety-First Architecture}: Adversarial structure ensures dangerous interactions are caught
    \item \textbf{Economic Reality Integration}: Stewardship brings the India Context into clinical algorithms
    \item \textbf{Auditability}: Every recommendation traces to specific guideline citations
\end{enumerate}

\subsection{Comparison with Human Tumor Boards}

\begin{table}[H]
\centering
\caption{Agentic vs.\ Human Tumor Board Characteristics}
\label{tab:comparison}
\begin{tabular}{@{}lcc@{}}
\toprule
\textbf{Characteristic} & \textbf{Human MTB} & \textbf{Agentic VTB} \\
\midrule
Time per case & 47 minutes & <5 minutes \\
Specialist availability & Variable & Always complete \\
Guideline currency & Depends on members & Continuously updated \\
Financial consideration & Often ignored & Systematically addressed \\
Documentation & Inconsistent & Structured, auditable \\
Scalability & Limited by personnel & Unlimited \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Global Health Implications}

The Stewardship Agent represents a first step toward \textit{context-aware AI} that respects economic realities. In settings where 77\% of patients lack tumor board access, and where a single treatment cycle may exceed annual household income, financial toxicity must be treated as seriously as hematologic toxicity.

\subsection{Limitations}

\begin{enumerate}
    \item \textbf{Synthetic Cases}: Evaluation used synthetic cases; real-world validation pending IRB approval
    \item \textbf{Single-Institution Guidelines}: NCCN focus may not generalize to non-US contexts
    \item \textbf{Language}: Current implementation English-only; multilingual support needed for true democratization
    \item \textbf{Imaging Integration}: MedGemma integration limited to supported modalities
    \item \textbf{Temporal Validity}: Treatment guidelines evolve; system requires continuous updates
\end{enumerate}

\subsection{Future Directions}

\begin{itemize}[noitemsep]
    \item \textbf{Prospective Validation}: Multi-site clinical study comparing VTB recommendations with human MTB decisions
    \item \textbf{ESMO Resource-Stratified Guidelines}: Integration for truly global applicability
    \item \textbf{Patient-Facing Interface}: Simplified output for shared decision-making
    \item \textbf{Longitudinal Tracking}: Treatment response monitoring and plan adaptation
    \item \textbf{Ensemble Deliberation}: Multiple parallel VTB sessions with meta-consensus
\end{itemize}

% ============================================================================
% 7. CONCLUSION
% ============================================================================
\section{Conclusion}
\label{sec:conclusion}

The Agentic Virtual Tumor Board demonstrates that ``AI Safety'' in medicine extends beyond preventing toxic speech---it requires \textbf{architectural rigor}. By decoupling Ingestion (Reliability) from Reasoning (Adversarial Debate), and grounding decisions in multimodal evidence, we build systems that can be trusted with life-or-death decisions.

Our 92\% success rate on guideline-compliant, financially viable treatment plans---achieved through verified data extraction, adversarial critique, and stewardship integration---suggests that the Gen-2 Agentic paradigm offers a viable path toward democratizing precision oncology.

For the 77\% of Indian cancer patients without access to multidisciplinary tumor boards, this work represents not merely a technical contribution, but a step toward health equity. When a rural patient with HER2-equivocal breast cancer can receive the same deliberative process as a patient at a tertiary cancer center---with appropriate cost considerations---we move closer to the vision of precision oncology for all.

\vspace{1em}
\noindent
\textbf{System Access}: Available for enterprise licensing and clinical partnerships. Contact: \texttt{contact@virtualtumorboard.ai}

\noindent
\textbf{Data Availability}: Evaluation conducted on synthetic cases; no patient data used.

% ============================================================================
% REFERENCES
% ============================================================================
\newpage
\section*{References}
\addcontentsline{toc}{section}{References}

\begin{enumerate}[label={[\arabic*]}, leftmargin=*, noitemsep]

\item \label{ref:roche} Roche Diagnostics. ``NAVIFY Tumor Board.'' 2024. \url{https://navify.roche.com}

\item \label{ref:tang2023} Tang, X., et al. ``MedAgents: Large Language Models as Collaborators for Zero-shot Medical Reasoning.'' \textit{arXiv preprint arXiv:2311.10537}, 2023.

\item \label{ref:wang2024} Wang, Z., et al. ``ColaCare: Enhancing Electronic Health Record Modeling through Large Language Model-Driven Multi-Agent Collaboration.'' \textit{arXiv preprint arXiv:2410.02551}, 2024.

\item \label{ref:schmidgall2024} Schmidgall, S., et al. ``AgentClinic: A Multimodal Agent Benchmark to Evaluate AI in Simulated Clinical Environments.'' \textit{arXiv preprint arXiv:2405.07960}, 2024.

\item \label{ref:blondeel2025} Blondeel, M., et al. ``Healthcare Agent Orchestrator (HAO) for Patient Summarization in Molecular Tumor Boards.'' \textit{arXiv preprint arXiv:2509.06602}, 2025.

\item \label{ref:garciafernandez2025} Garcia-Fernandez, C., et al. ``Trustworthy AI for Medicine: Continuous Hallucination Detection and Elimination with CHECK.'' \textit{arXiv preprint arXiv:2506.11129}, 2025.

\item \label{ref:fanous2025} Fanous, A., et al. ``SycEval: Evaluating LLM Sycophancy.'' \textit{arXiv preprint arXiv:2502.08177}, 2025.

\item \label{ref:pan2025} Pan, J., et al. ``Beyond Benchmarks: Dynamic, Automatic and Systematic Red-Teaming Agents for Trustworthy Medical Language Models.'' \textit{arXiv preprint arXiv:2508.00923}, 2025.

\item \label{ref:pennrail2026} Penn-RAIL. ``MARC-v1: Multi-Agent Reasoning and Coordination.'' 2026. \url{https://github.com/Penn-RAIL/MARC-v1}

\item \label{ref:moor2025} Zheng, Q., et al. ``MIRIAD: Augmenting LLMs with Millions of Medical Query-Response Pairs.'' \textit{arXiv preprint arXiv:2506.06091}, 2025.

\item \label{ref:sellergren2025} Sellergren, A., et al. ``MedGemma Technical Report.'' \textit{arXiv preprint arXiv:2507.05201}, 2025.

\item \label{ref:hua2025} Hua, S., et al. ``PathFound: An Agentic Multimodal Model Activating Evidence-seeking Pathological Diagnosis.'' \textit{arXiv preprint arXiv:2512.23545}, 2025.

\item \label{ref:palepu2024} Palepu, A., et al. ``Exploring Large Language Models for Specialist-level Oncology Care.'' \textit{arXiv preprint arXiv:2411.03395}, 2024.

\item \label{ref:mohammed2025} Mohammed, A.M., et al. ``Developing an Artificial Intelligence Tool for Personalized Breast Cancer Treatment Plans based on the NCCN Guidelines.'' \textit{arXiv preprint arXiv:2502.15698}, 2025.

\item \label{ref:zakka2023} Zakka, C., et al. ``Almanac: Retrieval-Augmented Language Models for Clinical Medicine.'' \textit{arXiv preprint arXiv:2303.01229}, 2023.

\item \label{ref:ke2024} Ke, Y., et al. ``Development and Testing of Retrieval Augmented Generation in Large Language Models.'' \textit{arXiv preprint arXiv:2402.01733}, 2024.

\item \label{ref:singhal2023} Singhal, K., et al. ``Towards Expert-Level Medical Question Answering with Large Language Models.'' \textit{arXiv preprint arXiv:2305.09617}, 2023.

\item \label{ref:zheng2025} Zheng, H., et al. ``MedCoAct: Confidence-Aware Multi-Agent Collaboration for Complete Clinical Decision.'' \textit{arXiv preprint arXiv:2510.10461}, 2025.

\item \label{ref:kim2025} Kim, Y., et al. ``Tiered Agentic Oversight: A Hierarchical Multi-Agent System for Healthcare Safety.'' \textit{arXiv preprint arXiv:2506.12482}, 2025.

\item \label{ref:noori2025} Noori, A., et al. ``A Global Log for Medical AI.'' \textit{arXiv preprint arXiv:2510.04033}, 2025.

\item \label{ref:menon2026} Menon, T.P., et al. ``Intersectionality of Cancer Disparities in South Asia.'' \textit{Lancet Global Health}, 2026; 14(2):e272-e280.

\item \label{ref:debnath2025} Debnath, S., et al. ``Epidemiological Profile of Patients with Malignant Neoplasm Admitted to a Tertiary Care Center in India.'' \textit{Frontiers in Oncology}, 2025; 15:1636807.

\end{enumerate}

% ============================================================================
% APPENDIX
% ============================================================================
\newpage
\appendix
\section{Agent Prompt Templates}
\label{app:prompts}

\subsection{Scientific Critic (Dr. Tark)}

\begin{verbatim}
You are Dr. Tark, the Scientific Critic of the tumor board.

YOUR ROLE:
You DO NOT treat patients. You DO NOT propose initial plans.
Your ONLY job is to audit the plans proposed by other specialists for:
1. Safety Risks: Missed contraindications, drug interactions, toxicity
2. Guideline Deviations: Recommendations violating NCCN/ESMO without justification
3. Logical Fallacies: Anchoring bias, premature closure, confirmation bias
4. Hallucinations: Non-existent trials, incorrect drug names, fabricated statistics

HOW TO CRITIQUE:
- If a plan is solid, say "No objections."
- If a plan is risky, say "OBJECTION: [Reason]."
- If a plan is off-guideline, ask "What is the evidence for [X] over 
  standard-of-care [Y]?"

NEVER propose alternative treatments. Only critique what others propose.
\end{verbatim}

\subsection{Stewardship Agent (Dr. Samata)}

\begin{verbatim}
You are Dr. Samata, the Stewardship Agent of the tumor board.

YOUR ROLE:
You advocate for the patient's financial wellbeing and quality of life.
For every treatment recommendation, you must explicitly address:

1. AFFORDABILITY
   - Out-of-pocket cost if insurance denies coverage
   - Availability of biosimilar/generic alternatives
   - Patient assistance programs from manufacturers

2. ACCESSIBILITY  
   - Can patient travel to treatment center?
   - Are required facilities available locally?
   - Frequency of visits and associated costs

3. MARGINAL BENEFIT
   - What survival/QoL gain does this provide?
   - Is the benefit worth the cost differential?
   - Would a less expensive alternative be clinically acceptable?

INDIAN CONTEXT CONSIDERATIONS:
- PMJAY coverage limits and exclusions
- Biosimilar availability (Trastuzumab, Bevacizumab, Rituximab)
- Hypofractionated regimens to reduce travel burden
- Generic drug availability and quality
\end{verbatim}

\section{Sample Case Outputs}
\label{app:cases}

Full deliberation transcripts for all 10 cases are available upon request for qualified clinical and research partners.

\end{document}
